TGI Spinal Analysis Code

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
recreating as box plots

# TRY THESE PLOTS WITH BOX JITTER? gghalves may be too messy

# plot all data - half-violins
# COLD
ggplot(data = vas_meds %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal')) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral')) +
  facet_wrap(~manipulation)

  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

# WARM
ggplot(data = vas_meds %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'warm'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'warm'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'warm'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(oran[4], oran[6])) +
  scale_fill_manual(values = c(oran[4], oran[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Warm ratings', x = 'Location of cold probe', 
         y = NULL) +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot

# BURN
ggplot(data = vas_meds %>% 
         filter(quality == 'burn'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum %>% 
               filter(quality == 'burn'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum %>% 
               filter(quality == 'burn'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum %>% 
              filter(quality == 'burn'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(purp[4], purp[6])) +
  scale_fill_manual(values = c(purp[4], purp[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Burn ratings', x = 'Location of cold probe', 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_burn_plot

# arrange entire plot
h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
                     nrow = 2, ncol = 2)
h2_plot

@@

# TRY THESE PLOTS WITH BOX JITTER? gghalves may be too messy

# plot all data - half-violins
# COLD
ggplot(data = vas_meds1 %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'cold'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'cold'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'cold'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(blue[4], blue[6])) +
  scale_fill_manual(values = c(blue[4], blue[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot

# WARM
ggplot(data = vas_meds1 %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'warm'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'warm'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'warm'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(oran[4], oran[6])) +
  scale_fill_manual(values = c(oran[4], oran[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Warm ratings', x = 'Location of cold probe', 
         y = NULL) +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot

# BURN
ggplot(data = vas_meds1 %>% 
         filter(quality == 'burn'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_point(shape = 21, alpha = .5, position = position_nudge(nudge2)) +
  geom_half_violin(
    data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'distal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'rostral'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  geom_half_violin(
    data = vas_meds1 %>% 
    filter(quality == 'burn', cold_probe == 'caudal'),
    aes(x = xj, y = VAS), 
    position = position_nudge(x = nudge1), side = "l", alpha = .4) +
  # summary stats
  geom_point(data = h2_sum1 %>% 
               filter(quality == 'burn'), 
             aes(x = as.numeric(cold_code), y = VAS),
             shape = 21, size = 2, colour = 'grey20', fill = 'grey30',
             position = position_nudge(nudge1)) +
  geom_errorbar(data = h2_sum1 %>% 
               filter(quality == 'burn'), 
               aes(x = as.numeric(cold_code), ymin = VAS-ci, ymax = VAS+ci),
               colour = 'grey20', width = .05, size = .7,
               position = position_nudge(nudge1)) +
  geom_line(data = h2_sum1 %>% 
              filter(quality == 'burn'), 
              aes(x = as.numeric(cold_code), y = VAS), 
              colour = 'grey20', size = .7, alpha = .6,
              position = position_nudge(nudge1)) +
  facet_wrap(~manipulation) +
  scale_colour_manual(values = c(purp[4], purp[6])) +
  scale_fill_manual(values = c(purp[4], purp[6])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('prox.','dist.','rost.','caud.')) +
  labs(title = 'Burn ratings', x = 'Location of cold probe', 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_burn_plot

>>>>

# plot all data
# COLD
ggplot(data = vas_meds %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  scale_colour_manual(values = c(blue[5], blue[7])) +
  scale_fill_manual(values = c(blue[2], blue[4])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot
h2_cold_plot

# WARM
ggplot(data = vas_meds %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  scale_colour_manual(values = c(oran[5], oran[7])) +
  scale_fill_manual(values = c(oran[2], oran[4])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
  labs(title = 'Warm ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot

# BURN
ggplot(data = vas_meds %>% 
         filter(quality == 'burn'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'proximal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'distal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'rostral', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds %>% 
    filter(quality == 'burn', cold_probe == 'caudal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  scale_colour_manual(values = c(purp[5], purp[7])) +
  scale_fill_manual(values = c(purp[2], purp[4])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
  labs(title = 'Burn ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none')  -> h2_burn_plot

# arrange entire plot
h2_plot <- ggarrange(h2_cold_plot, h2_warm_plot, h2_burn_plot,
                     nrow = 2, ncol = 2,
                     common.legend = TRUE)
h2_plot

@@

# plot all data
# COLD
ggplot(data = vas_meds1 %>% 
         filter(quality == 'cold'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'proximal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'distal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'rostral', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'cold', cold_probe == 'caudal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  scale_colour_manual(values = c(blue[5], blue[7])) +
  scale_fill_manual(values = c(blue[2], blue[4])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
  labs(title = 'Cold ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_cold_plot
h2_cold_plot

# WARM
ggplot(data = vas_meds1 %>% 
         filter(quality == 'warm'),
       mapping = aes(x = xj, y = VAS, colour = manipulation, fill = manipulation)) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'proximal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'distal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'rostral', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'Non-TGI'),
    position = position_nudge(x = nudge1), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  geom_boxjitter(data = vas_meds1 %>% 
    filter(quality == 'warm', cold_probe == 'caudal', manipulation == 'TGI'),
    position = position_nudge(x = nudge2), width = .2,
      errorbar.length = .2, jitter.shape = 21, jitter.size = 1.5,
      outlier.shape = NA, errorbar.draw = TRUE, lwd = 0.7) +
  scale_colour_manual(values = c(oran[5], oran[7])) +
  scale_fill_manual(values = c(oran[2], oran[4])) +
  scale_x_continuous(breaks = c(1,2,3,4), labels = c('proximal','distal','rostral','caudal')) +
  labs(title = 'Warm ratings', x = NULL, 
         y = 'VAS Rating (0-100)') +
  ylim(-0.5,100) +
  theme_classic() +
  theme(legend.position = 'none') -> h2_warm_plot
